---
title: "AS10-0B：文字分析的法務應用"
author: "卓雍然 D994010001"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

<br>

```{r}
packages = c(
  "dplyr","ggplot2","caTools","tm","SnowballC","ROCR","rpart","rpart.plot","randomForest")
existing = as.character(installed.packages()[,1])
for(pkg in packages[!(packages %in% existing)]) install.packages(pkg)
```

```{r warning=F, message=F, cache=F, error=F}
rm(list=ls(all=TRUE))
Sys.setlocale("LC_ALL","C")
options(digits=5, scipen=10)

library(dplyr)
library(tm)
library(SnowballC)
library(ROCR)
library(caTools)
library(rpart)
library(rpart.plot)
library(randomForest)
```
<br><hr>


```{r}
emails = read.csv("data/energy_bids.csv", stringsAsFactors=FALSE)
```

##### Look at emails
```{r}
emails$email[1]
emails$responsive[1]
emails$email[2]
emails$responsive[2]
```

##### Ratio of Responsive emails
```{r}
mean(emails$responsive)
```

##### Create and Prepare Corpus
```{r}
library(tm)
txt <- iconv(enc2utf8(emails$email),sub="byte")
corpus = Corpus(VectorSource(txt))
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, removeWords, stopwords("english"))
corpus = tm_map(corpus, stemDocument)
corpus[[1]]$content
```

##### Document Term Matrix
```{r}
# create dtm
dtm = DocumentTermMatrix(corpus); dtm
```

```{r}
# Remove sparse terms
dtm = removeSparseTerms(dtm, 0.97); dtm
```

##### Prepare Data Frame 
```{r}
# Create data frame
labeledTerms = as.data.frame(as.matrix(dtm))

# Add in the outcome variable
labeledTerms$responsive = emails$responsive
```

##### Prepare Train & Test Data
```{r}
library(caTools)
set.seed(144)
spl = sample.split(labeledTerms$responsive, 0.7)
train = subset(labeledTerms, spl == TRUE)
test = subset(labeledTerms, spl == FALSE)
```

### CART Model

##### Modeling
```{r}
# Build a CART model
library(rpart)
library(rpart.plot)
emailCART = rpart(responsive~., data=train, method="class")
prp(emailCART)
```

##### Predicting
```{r}
# Make predictions on the test set
pred = predict(emailCART, newdata=test)
pred[1:10,]
pred.prob = pred[,2]
```

##### Validating Accuracy
```{r}
# Compute accuracy
table(test$responsive, pred.prob >= 0.5) %>% {sum(diag(.))/sum(.)}
```

```{r}
# Baseline model accuracy
1- mean(test$responsive)
```

##### ROC
```{r fig.height=4, fig.width=4}
# ROC curve
library(ROCR)
predROCR = prediction(pred.prob, test$responsive)
perfROCR = performance(predROCR, "tpr", "fpr")
par(mar=c(6,5,3,3),cex=0.8)
plot(perfROCR, colorize=TRUE)
```

##### AUC
```{r}
performance(predROCR, "auc")@y.values   # AUC = 0.7964
colAUC(pred[,2], test$responsive)
```
<br><hr>

<p class="qiz">
討論議題：<br>
&emsp; ■ 在這個應用裡面你認為TFP和FPR哪樣比較重要呢？ <br>
&emsp; &emsp; ● 為甚麼？ <br>
&emsp; &emsp; ● 什麼因素會決定TFP和FPR的相對重要性？ <br>
&emsp; &emsp; ● 有什麼方法可以量化TFP和FPR的相對重要性？ <br>
&emsp; &emsp; ● <br>
<br>
&emsp; ■ 根據這條ROC曲線你會如何決定你的臨界機率呢？ <br>
&emsp; &emsp; ● 你為什麼會做這個決定？ <br>
&emsp; &emsp; ● <br>
<br>
</p>

<br><br><br><br>





